Ecosystem size and complexity dictate riverine biodiversity

### 2021-01-05 manuscript.Rmd
Updates

Similarly, we found weak to moderate supports for the global models explaining observed patterns of $\alpha$ and $\beta$ diversity (Bayes factor: `r round(fit$alpha$bayes_factor, 1)` and `r round(fit$beta$bayes_factor, 1)`, respectively). In both regions, $\beta$ diversity responded significantly to ecosystem size and complexity. In our simulations, this pattern has emerged under the scenarios with dispersal limitation, which elegantly match the previous observations of stream fish movement. Direct (mark-recapture) and indirect observations (e.g., genotyping) recurrently revealed restricted movement of stream fish, typically limited to several tens to hundreds of meters in distance[@comteFishDispersalFlowing2018; @radingerPatternsPredictorsFish2014; @rodriguezRestrictedMovementStream2002]. The reciprocal agreement of theoretical and empirical patterns provides indirect but convincing evidence that dispersal limitation plays a key role in driving the associations between $\gamma$ diversity and ecosystem properties in rivers.

@@

### Simulation
We used `r n_scenario` sets of parameter combinations to produce different landscape (four patterns of habitat heterogeneity) and ecological scenarios (eight patterns of dispersal and competition). To create landscape scenarios with different patterns of habitat heterogeneity, we varied environmental variation at headwaters ($\sigma_h$) and the degree of local environmental noise ($\sigma_l$) separately. Larger values of $\sigma_h$ and/or $\sigma_l$ produce greater variation in environmental conditions among habitat patches. We used two values for each of the SD parameters ($\sigma_h =$ `r unique(dat_sim$sd_env_source)` and $\sigma_l =$ `r unique(dat_sim$sd_env_lon)`), resulting in four sets of parameter combinations. When $\sigma_h > \sigma_l$, having more tributaries in a network exhibits important effects on overall habitat diversity as branching is the primary source of environmental variation. When $\sigma_h \le \sigma_l$, local environmental noise masks environmental variation among tributaries, leading to minimal influences of branching on overall habitat diversity in a network. For ecological scenarios, we varied three ecological parameters that are relevant for dispersal and interspecific competition: dispersal distance ($\theta =$ `r unique(dat_sim$theta)`), dispersal probability ($p_d =$ `r unique(dat_sim$p_dispersal)`), and the maximum value of competition coefficients ($\alpha_{max} =$ `r unique(dat_sim$max_alpha)`). This setup results in eight ecological scenarios with different levels of dispersal and competition.

@@

We estimated $\alpha$, $\beta$ and $\gamma$ diversity at each watershed. $\gamma$ diversity is the total species richness at each watershed. Since it is impossible to sample all species present in each watershed, we used asymptotic species richness as a proxy for $\gamma$ diversity. Asymptotic species richness is the estimated total species richness in a given area and can be estimated from spatial replicates of local community data within a metacommunity. We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity). We assessed the completeness of the observed species richness based on sample coverage, which is the proportion of observed species richness to asymptotic species richness. We excluded watersheds whose sample coverage was below 0.9 because the estimates of asymptotic species richness may contain non-negligible statistical uncertainty. $\alpha$ diversity was estimated by taking an average of local species richness at each site. $\beta$ diversity was estimated by dividing the estimated $\gamma$ diversity by $\alpha$ diversity.

After the data selection procedure, we obtained diversity estimates from `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (Hokkaido: `r nrow(wsd_subset[[1]])`, Midwest: `r nrow(wsd_subset[[2]])`), which encompassed a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites (Hokkaido: `r nrow(point_subset[[1]])`, Midwest: `r nrow(point_subset[[2]])`).

>>>>

Similarly, we found weak to moderate supports for the global models of $\alpha$ and $\beta$ diversity (Bayes factor: `r round(fit$alpha$bayes_factor, 1)` and `r round(fit$beta$bayes_factor, 1)`, respectively). In both regions, $\beta$ diversity responded significantly to ecosystem size and complexity. In our simulations, this pattern has emerged under the scenarios with dispersal limitation, which elegantly match the previous observations of stream fish movement. Direct (mark-recapture) and indirect observations (e.g., genotyping) recurrently revealed restricted movement of stream fish, typically limited to several tens to hundreds of meters in distance[@comteFishDispersalFlowing2018; @radingerPatternsPredictorsFish2014; @rodriguezRestrictedMovementStream2002]. The reciprocal agreement of theoretical and empirical patterns provides indirect but convincing evidence that dispersal limitation plays a key role in driving the associations between $\gamma$ diversity and ecosystem properties in rivers.

@@

### Simulation
We used `r n_scenario` sets of parameter combinations to produce different landscape (four patterns of habitat heterogeneity) and ecological scenarios (eight patterns of dispersal and competition). To create landscape scenarios with different patterns of habitat heterogeneity, we varied environmental variation at headwaters ($\sigma_h$) and the degree of local environmental noise ($\sigma_l$) separately. Larger values of $\sigma_h$ and/or $\sigma_l$ produce greater variation in environmental conditions among habitat patches. We used two values for each of the SD parameters ($\sigma_h =$ `r unique(dat_sim$sd_env_source)` and $\sigma_l =$ `r unique(dat_sim$sd_env_lon)`), resulting in four sets of parameter combinations. When $\sigma_h > \sigma_l$, having more tributaries in a network exhibits important effects on overall habitat diversity as branching is the primary source of environmental variation. When $\sigma_h \le \sigma_l$, local environmental noise masks environmental variation among tributaries, leading to minimal influences of branching on overall habitat diversity in a network.

For ecological scenarios, we varied three ecological parameters that are relevant for dispersal and interspecific competition: dispersal distance ($\theta =$ `r unique(dat_sim$theta)`), dispersal probability ($p_d =$ `r unique(dat_sim$p_dispersal)`), and the maximum value of competition coefficients ($\alpha_{max} =$ `r unique(dat_sim$max_alpha)`). This setup results in eight ecological scenarios with different levels of dispersal and competition.

@@

We estimated $\alpha$, $\beta$ and $\gamma$ diversity at each watershed. $\gamma$ diversity is the total species richness at each watershed. Since it is impossible to sample all species present in each watershed, we used asymptotic species richness as a proxy for $\gamma$ diversity. Asymptotic species richness can be interpreted as the estimated true species richness in a given area when it is estimated using spatial replicates of local community data within a metacommunity[@chaoRarefactionExtrapolationHill2014a; @chaseEcosystemDecayExacerbates2020]. We estimated asymptotic species richness using sampling sites located in the same watershed (i.e., spatial replicates within a metacommunity) via an R package iNEXT[@hsiehINEXTPackageRarefaction2016]. We assessed the completeness of the observed species richness based on sample coverage, which is the proportion of observed species richness to asymptotic species richness. We excluded watersheds whose sample coverage was below 0.9 because the estimates of asymptotic species richness may contain non-negligible statistical uncertainty. $\alpha$ diversity was estimated by taking an average of local species richness at each site. $\beta$ diversity was estimated by dividing the estimated $\gamma$ diversity by $\alpha$ diversity.

After the data selection procedure, we obtained diversity estimates from `r nrow(wsd_subset[[1]]) + nrow(wsd_subset[[2]])` watersheds (Hokkaido: `r nrow(wsd_subset[[1]])`, Midwest: `r nrow(wsd_subset[[2]])`), which encompassed a total of `r nrow(point_subset[[1]]) + nrow(point_subset[[2]])` sites (Hokkaido: `r nrow(point_subset[[1]])`, Midwest: `r nrow(point_subset[[2]])`). We used this dataset for statistical analysis.
